Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-02-05 paperIEEE.tex
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@101 db7c848b-7755-4df2-b763-8796797afa52

We tested the decomposition modes with both volume (\fig{fBenchmarkEVolve}) and polygonal data  (\fig{fBenchmarkEqPly}) and used test scenes that allowed us to finely adjust the rendering load the system has to cope with. In both cases the scene comprised of two rows of instantiated, identical models (the 1mm David model when rendering polygonal data, the $1024^3$ Flower model when rendering volumes), with 30 models in total. Rendering was performed
% with the \textsf{Equalizer} example applications eqPly (for meshes) and eVolve (for volumes)
at 2560x1440. The camera is initially placed in the center of the scene, between the two rows. It is then moved backward over the duration of 800 frames, steadily increasing the rendering load by revealing more and more model instances.

@@

In the case of volume rendering we also measured the performance of compounds under heterogeneous load, which was easily achievable by varying the number of volume samples used for each fragment (1-8), while rendering. This allowed for a consistent linear scaling of rendering load, which was randomly varied (\fig{fEqualizers}) either per frame or per node. Such a linear scaling of load per node corresponds to a scaling of resources, e.g., doubling the rendering load on a specific node corresponds to halving the available rendering resources. This node would then only contribute the value 0.5 in terms of {\em normalized compute resources} to the system, as illustrated by \fig{fEqualizers}.

>>>>

We tested the decomposition modes with both volume (\fig{fBenchmarkEVolve}) and polygonal data  (\fig{fBenchmarkEqPly}) and used test scenes that allowed us to finely adjust the rendering load the system has to cope with. In both cases the scene comprised of two rows of instantiated, identical models (the 1mm David model when rendering polygonal data, the $1024^3$ Flower model when rendering volumes), with 30 models in total. Rendering was performed
% with the \textsf{Equalizer} example applications eqPly (for meshes) and eVolve (for volumes)
at 2560x1440. The camera is initially placed in the center of the scene, between the two rows (\fig{fBenchmarkEVolve} and \fig{fBenchmarkEqPly}), rendering only half of the model instances. It is then moved backward over the duration of 800 frames, steadily increasing the rendering load by revealing more models, until all 30 instances are visible.

@@

In the case of volume rendering we also measured the performance of compounds under heterogeneous load, which was easily achievable by varying the number of volume samples used for each fragment (1-7), while rendering. This allowed for a consistent linear scaling of rendering load, which was randomly varied (\fig{fEqualizers}) either per frame or per node. Such a linear scaling of load per node corresponds to a scaling of resources, e.g., doubling the rendering load on a specific node corresponds to halving its available rendering resources. To the system this node would then contribute the value 0.5 in terms of {\em normalized compute resources}, as illustrated by \fig{fEqualizers} (left).

This figure gives an impression of how individual compounds perform on heterogeneous systems. In this case the tree equalizer compound performs best (\fig{fEqualizers} (left)), as it allows us to a priori define how much {\em usage} it should make of individual rendering nodes, in accordance with the expected load / the available compute resources. \fig{fEqualizers} (right), on the other hand, illustrates how compounds perform on a system where compute resources fluctuate randomly every frame, as can arguably be the case for cloud-based applications. For this scenario tile equalizer seems best suited, as it performs load balancing implicitly and does not assume coherence of available resources between frames.
